Global patterns of forest autotrophic carbon fluxes

### 2020-08-05 manuscript/manuscript draft.Rmd
slightly condensed results

We next examined the relationships of C fluxes to climate variables (Q2-Q4; Table 1). 
We tested first-order linear, second-order polynomial, and logarithmic fits for each climate variable. 
Again, polynomial fits were considered superior to first-order linear fits only if inclusion of a second-order polynomial term resulted in $\Delta$ AIC $\ge$ 2.0 relative to a first-order linear model.
We tested relationships of each C flux (Table 2) against each climate variable (Table S1), but focus presentation--including focal hypotheses (Table 1)--on climate variables that explained >20% of variation in C fluxes.

**Becky, please make this more specific. I drafted this based on the results, but its not very clear.** **BBL: I agree, not clear and might trigger reviewer concerns about tailoring hypotheses to significance.**

@@

All fluxes increased with MAT (all p<0.05; Figs. 3-4, S4-S5, Table S2). 
For eight of the nine fluxes, this relationship was linear.
For only one variable, $BNPP$, did a lognormal fit provide signficant improvement over a first-order linear relationship. 
*As with latitude, MAT tended to explain more variation in the larger flux ($GPP$, $NPP$, $ANPP$, $R_{auto}$) and $ANPP_{foliage}$ (all $R^2$> 0.4) than in subsidiary and belowground fluxes ($ANPP_{stem}$, $R_{root}$, $BNPP_{fine.root}$; all $R^2$< 0.25).* **update this NB these values are correct**

MAP was a significant (p<0.05) predictor of all fluxes (Figs. 4a, S4-S5; Table S2). 
However, it explained little variation: with the exception of $R_{auto}$, MAP explained at most 25% of variation in C flux. 
For five of the nine fluxes, a second-order polynomial model provided the best fit, while first-order linear and lognormal relationships provided each provided the best fit for two flxues. 
All fluxes increased with MAP up to at least 2000 mm, above which responses were variable (Figs. 4, S4-S5).

@@

All C flux variables were significantly related to potential evapotranspiration. $ANPP_{foliage}$, $BNPP_{fine.root}$ and $R_{root}$ increased linearly with PET; however, all other fluxes showed a polynomial relationship with PET (Fig. 4c, S4-5; Table S2). We found strong evidence for a saturation point or peak with PET: C fluxes tended to increase at values below 1000mm, before saturating between 1200 and 1700mm. There was also evidence that some C fluxes begin to decrease at values above 1800mm PET.

Vapour pressure deficit was a significant predictor of all C fluxes. $BNPP_{fine.root}$ showed a linear relationship with vapour pressure deficit ($R^2$ = 0.07, p<0.05), but all other fluxes showed a polynomial relationship (Figs. 4d, S4-5; Table S2). 
C fluxes initially increased with vapour pressure deficit, before saturating at around 0.8 kPa, after which point they began to decrease.

All fluxes, with the exception of $R_{root}$, showed a positive linear relationship with solar radiation (Figs. S4-S5, Table S2). Solar radiation explained a low proportion of variability in all C fluxes, explaining less than 20% of the variation in each flux, with the exception of $R_{auto}$ ($R^2$ = 0.26, p<0.05).

Annual wet days, cloud cover, and aridity were poor or non-significant explainers of variation in C fluxes, explaining less than 20% of the variation in each of the carbon fluxes (Figs. S4-S5; Table S2).

@@

Temperature seasonality was a strong predictor of annual C fluxes. $GPP$ showed a polynomial relationship with seasonality **(update this paragraph based on new results)**
$GPP$, $NPP$, $ANPP$, and $R_{root}$ exhibited a polynomial relationship with seasonality (all p<0.05; Figs. 4e, S6-7; Table S2). $ANPP_{foliage}$, $ANPP_{stem}$ and $R_{auto}$ decreased linearly with temperature seasonality (all p<0.05; Figs. 4e, S6-S7; Table S2). Temperature seasonality was strongly correlated with annual temperature range, which was likewise a similarly strong predictor of C fluxes (Table S2). 
C fluxes were highest where temperature seasonality = 0, and at an annual temperature range of 15$^\circ$C or lower. **BBL: perhaps put this into an ecosystem context; what are these? Aseasonal subtropical places?**

>>>>

We next examined the relationships of C fluxes to climate variables (Q2-Q4; Table 1). 
We tested first-order linear, second-order polynomial, and logarithmic fits for each climate variable. 
Again, polynomial fits were considered superior to first-order linear fits only if inclusion of a second-order polynomial term resulted in $\Delta$ AIC $\ge$ 2.0 relative to a first-order linear model.
We tested relationships of each C flux (Table 2) against each climate variable (Table S1). Variables which were not significant explanatory variables or which explained <20% of variation in C fluxes are only presented in SI.

@@

All fluxes increased with MAT (all p<0.05; Figs. 3-4, S4-S5, Table S2). 
For eight of the nine fluxes, this relationship was linear.
For only one variable, $BNPP$, did a lognormal fit provide signficant improvement over a first-order linear relationship. 
*As with latitude, MAT tended to explain more variation in the larger flux ($GPP$, $NPP$, $ANPP$, $R_{auto}$) and $ANPP_{foliage}$ (all $R^2$> 0.4) than in subsidiary and belowground fluxes ($ANPP_{stem}$, $R_{root}$, $BNPP_{fine.root}$; all $R^2$< 0.25).* **update this -- NB these values are correct**

MAP was a significant (p<0.05) predictor of all fluxes (Figs. 4a, S4-S5; Table S2). 
However, it explained little variation: with the exception of $R_{auto}$, MAP explained at most 25% of variation in C flux. 
For five of the nine fluxes, a second-order polynomial model provided the best fit, while first-order linear and lognormal relationships each provided the best fit for two flxues. 
All fluxes increased with MAP up to at least 2000 mm, above which responses were variable (Figs. 4, S4-S5).

@@

All C flux variables were significantly related to potential evapotranspiration. $ANPP_{foliage}$, $BNPP_{fine.root}$ and $R_{root}$ showed a logarithmic relationship with PET; however, all other fluxes showed a polynomial relationship with PET (Fig. 4c, S4-5; Table S2). We found strong evidence for a saturation point or peak with PET: C fluxes tended to increase at values below 1000mm, before saturating between 1200 and 1700mm. There was also evidence that some C fluxes begin to decrease at values above 1800mm PET.

Vapour pressure deficit was a significant predictor of all C fluxes. $ANPP_{foliage}$, $BNPP_{fine.root}$ and $R_{root}$ showed a logarithmic relationship with vapour pressure deficit, but all other fluxes showed a polynomial relationship (Figs. 4d, S4-5; Table S2). 
C fluxes initially increased with vapour pressure deficit, before saturating at around 0.8 kPa, after which point they began to decrease.

All fluxes, with the exception of $R_{root}$, showed a significant positive relationship with solar radiation (Figs. S4-S5, Table S2). Solar radiation explained a low proportion of variability in all C fluxes, explaining less than 30% of the variation in each flux

Annual wet days, cloud cover, aridity, and water stress months were poor or non-significant explainers of variation in C fluxes, explaining less than 20% of the variation in each of the carbon fluxes (Figs. S4-S5; Table S2).

@@

Temperature seasonality was a strong predictor of annual C fluxes. All fluxes decrease with increasing seasonality, though the shape of this relationship varies (all p<0.05; Figs. 4e, S6-7; Table S2). Temperature seasonality was strongly correlated with annual temperature range, which was likewise a similarly strong predictor of C fluxes (Table S2). 
C fluxes were highest where temperature seasonality = 0, and at an annual temperature range of 15$^\circ$C or lower. **BBL: perhaps put this into an ecosystem context; what are these? Aseasonal subtropical places?**
